\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 prelims.tex
.

@@

We define the PWA transition system as a discrete transition system
$\rho:\tupleof{\pLocs,\vx,\scrT, \pLocI,\Theta}$, where $\pLocs$ is
a nonempty set of locations, $\vx$ is a set of variables, $\scrT$
is a finite set of transitions of the form $\tupleof{l, \tau,
l'}$, where $l\in\pLocs$ is the pre-location, $l'\in\pLocs$ the
post-location and $\tau(\vx,\vx') \in \scrT$ is the transition. $\tau$
is labled by the transition relation $\rho_{\tau}$
over the current states and the next states. The transition relation
is defined in terms of affine predicates on the current and next
states and an affine update between them.
\[
    \rho_{\tau}(\vx,\vx') \subseteq \setof{(\vx,\vx')) \;|\;
    g_\tau(\vx) \land g'_\tau(\vx') \land f_{\tau}(\vx, \vx')}
\]
where $f_{\tau}$ is an affine relation on the pre and post states
$\vx,\vx'$, $g_{\tau}$ and $g'_{\tau}$ are affine guards (pre and
post conditions) on the states. Finally, $\pLocI$ is an initial
location $\Theta$ is an affine assertion characterizing the initial
states included in $\pLocI$.

>>>>

We define the PWA transition system as a discrete transition system
$\rho:\tupleof{\pLocs,\vx,\scrT, \pLocI,\Theta}$, where $\pLocs$ is
a nonempty set of locations, $\vx$ is a set of variables, $\scrT$
is a finite set of transitions of the form $\tupleof{l, \tau,
l'}$, where $l\in\pLocs$ is the pre-location, $l'\in\pLocs$ the
post-location and $\tau \in \scrT$ is the transition. $\tau$
is labled by the transition relation $\rho_{\tau}$
over the current states and the next states. The transition relation
is defined in terms of affine predicates on the current and next
states and an affine update between them.
\[
    \rho_{\tau}(\vx,\vx') \subseteq \setof{(\vx,\vx')) \;|\;
    g_\tau(\vx) \land g'_\tau(\vx') \land f_{\tau}(\vx, \vx')}
\]
where $f_{\tau}$ is an affine relation on the pre and post states
$\vx,\vx'$, $g_{\tau}$ and $g'_{\tau}$ are affine guards (pre and
post conditions) on the states. Finally, $\pLocI$ is an initial
location $\Theta$ is an affine assertion characterizing the initial
states included in $\pLocI$.

@@
